\documentclass[margin]{res}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Dr. Robert Mackenzie}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.5\hoffset\centerline{07894911233}
\moveleft.5\hoffset\centerline{rmackenzie8@gmail.com}

\begin{resume}

\section{EDUCATION}
	{\sl PhD,} Pharmacy \hfill 2014 \\
	University of Nottingham \\
	Thesis: Computational modeling of drug-polymer nanoparticles \\
	\\
        {\sl BSc, 2:1,} Biochemistry \hfill 2010 \\
        University of Bristol
 
\section{EXPERIENCE}
	{\sl Senior Site Reliability Engineer} \hfill September 2018 - present \\
        Sky 
        \begin{itemize} \itemsep -2pt
	\item Currently working with two separate vendors to design and
	integrate their Kubernetes-based OTT live streaming platforms.
	\item Provide on-call support for multiple platforms including
	Sky's DRM headend, ELK streaming analytics, a VM/hardware streaming
	platform and the new Kubernetes platform. Recent peak concurrency of
	1 million users.
        \end{itemize}
	{\sl DevOps Engineer} \hfill May 2016 \\
        Sky 
        \begin{itemize} \itemsep -2pt
	\item Implemented automation from the ground up. Puppet, Jenkins
	and Terraform allowed us to replace physical hardware from vendors
	with VMs to improve supportability and scale the platform.
	\item Helped the Streaming DevOps team grow from just me to
	10 engineers. This required me to train new recruits using
	documentation and white board sessions.
        \end{itemize}
	{\sl Associate DevOps Engineer} \hfill October 2014 \\
        Sky 
        \begin{itemize} \itemsep -2pt
	\item Used Django, Angular, Neo4J and PostgresQL to help create
	tools to improve Sky's recommendation engines.
        \end{itemize}

\section{SKILLS}
	{\sl Languages:} Puppet, Bash, Ruby, Groovy, Python, Ansible, Scala \\
	{\sl Software:} Kubernetes, Docker, VMware, Terraform, Jenkins, F5 GTM,
	Varnish, ELK, Prometheus, Grafana, Git, Crucible, Jira, Confluence \\
        {\sl Operating Systems:} RHEL/CentOS 6 + 7 \\
 
\section{AWARDS}
	{\sl Sky Believe in Better Award} \hfill 2017 \\
	Awarded to the Streaming Team for exceptional video quality KPIs that year. \\
	\\
	{\sl 2nd Place at Sky Hackathon} \hfill 2016 \\
	Worked in a team to generate bespoke linear channels from VOD content using python and an Ooyala API. \\
	\\
	{\sl Published academic research paper from my PhD} \hfill 2015 \\
	\\
	{\sl Most improved at Sky DevOps Bootcamp} \hfill 2014 \\
	Worked in a team to deploy web apps to AWS using git.

\end{resume}
\end{document}

